---
title: "`sfnetworks`: Tidy Geospatial Networks in R"
subtitle: "SICSS - Covenant: The Summer Institutes in Computational Social Science"
author: "Lucas van der Meer, Lorena Abad, *Andrea Gilardi*, Robin Lovelace"
date: "2022-06-27"
output:
  xaringan::moon_reader:
    includes:
      after_body: insert-logo.html
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      beforeInit: ["https://platform.twitter.com/widgets.js", "macro.js"]
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: 16:9
---
class: center, middle, hide-logo

```{r setup, include = FALSE, cache = FALSE}
# This is the recommended set up for flipbooks
# you might think about setting cache to TRUE as you gain practice --- building flipbooks from scratch can be time consuming
options(width = 70, pillar.print_min = 5L, digits = 4)
knitr::opts_chunk$set(
  dev.args = list(bg = 'transparent'),
  fig.width = 12, message = TRUE, fig.showtext = TRUE,
  warning = FALSE, comment = "", cache = TRUE, fig.retina = 3
)
knitr::opts_knit$set(global.par = TRUE)
Sys.setenv(`_R_S3_METHOD_REGISTRATION_NOTE_OVERWRITES_` = "false")
library(flipbookr)
library(xaringanthemer)
library(sf)
library(sfnetworks)
library(tidygraph)
library(igraph)
library(tidyverse)
```

```{r xaringan-themer, include = FALSE, cache = FALSE}
style_mono_accent(
  # hex color should be provided, or theme_xaringan doesn't work
  base_color = '#ffa500', #orange
  title_slide_background_image = "figs/milano.png",
  background_image = "figs/milano_bg.png",
  code_font_size = '17px',
  text_font_size = '23px',
  text_slide_number_color = '#b3b3b3', #grey70
  link_color = '#ff4500', #orangered  
  footnote_font_size = '0.5em',
  footnote_position_bottom = "30px",
  code_highlight_color = "#ffedcc", #faded-orange
  extra_css = list(
    ".pull-left-80" = list("float" = "left", "width" = "75.2%"),
    ".pull-left-70" = list("float" = "left", "width" = "65.8%"),
    ".pull-left-60" = list("float" = "left", "width" = "56.4%"),
    ".pull-left-50" = list("float" = "left", "wdith" = "50%"),
    ".pull-left-40" = list("float" = "left", "width" = "37.6%"),
    ".pull-left-30" = list("float" = "left", "width" = "28.2%"),
    ".pull-right-70" = list("float" = "right", "width" = "65.8%"),
    ".pull-right-60" = list("float" = "right", "width" = "56.4%"),
    ".pull-right-50" = list("float" = "right", "width" = "50.0%"),
    ".pull-right-40" = list("float" = "right", "width" = "37.6%"),
    ".pull-right-30" = list("float" = "right", "width" = "28.2%"),
    ".pull-right-30" = list("float" = "right", "width" = "20%"),
    ".orange" = list("color" = "#ffa500"),
    ".note" = list("font-size" = "0.8em", "position" = "absolute", 
      "bottom" = "30px", "padding-right" = "4em")
  )
)
```

```{r color, echo = FALSE, results='asis', cache = FALSE}
# crayon needs to be explicitly activated in Rmd
options(crayon.enabled = TRUE)
# Hooks needs to be set to deal with outputs
# thanks to fansi logic
old_hooks <- fansi::set_knit_hooks(
  knitr::knit_hooks,
  which = c("output", "message", "error")
)
```

### About me...

--

Research fellow in Statistics at the [University of Milano - Bicocca](https://en.unimib.it/), [Department of Economics, Management and Statistics](https://dems.unimib.it/en). 

---
class: center, middle, hide-logo

## Let's start!

The slides can be found here: https://sfnetworks.github.io/SICSS-Covenant/slides

The code to create them can be found here: https://github.com/sfnetworks/SICSS-Covenant

???

Don't forget to copy the links in chat! 

---
class: middle, hide-logo

## Schedule 

- 9.15 - 9.35: Brief introduction to the R package `sfnetworks`. 
  * What are Geospatial Networks?
  * Motivations and philosophy behind `sfnetworks`
- 9.35 - 9.45: Showcase the main preprocessing functions
- 9.45 - 10.15: Live demo. Click on [sfnetworks-demo.R](https://github.com/sfnetworks/SICSS-Covenant/raw/master/sfnetworks-demo.R) to download the R script. 
- 10.15 - 10.30: Q&A or extra examples. 

You can install the stable version of `sfnetworks` from [CRAN](https://CRAN.R-project.org/package=sfnetworks) and the development version from the [develop](https://github.com/luukvdmeer/sfnetworks/tree/develop) branch of the github repo: 

```{r, eval = FALSE}
remotes::install_github("luukvdmeer/sfnetworks", "develop")
```

???

Again, don't forget to copy the links in chat!
